### 2018-05-04 papers/synth/fig-yeast-vts.tex
my fusion added

% \newenvironment{psmallmatrix}
%   {\left(\begin{smallmatrix}}
%   {\end{smallmatrix}\right)}

@@

  \path (ic) edge node [below] {\^{Qc6}} (ga);
  \path (er) edge[bend right=20] node [right] {\^{Qc6}} (ic);

  %er <> ga
  \path (er) edge[bend right=20] node [left] {\^{Qc6}} (ga);
  \path (er) edge[bend left=20] node [left] {R6} (ga);
  \path (ga) edge[bend right=40] node [left] {\^{Qc1}} (er);

  %ga <-> ee
  \path (ga) edge[bend left=25] node [above] {Qb2 Qc2} (ee);
  \path (ga) edge[bend left=10] node [above] {Qbc2/3} (ee);
  \path (ee) edge[bend left=0] node [below] {Qb2/3,Qa2,R2,\^{R4},Qc2/3} (ga);

  %le <-> pm
  \path (le) edge[bend right=10] node [above] {Qb7 Qc7} (pm);
  %ee -> le
  \path (ee) edge[bend right] node [below,rotate=70] {\^{R8},Qa7,Qbc7,R7} (le);

  %pm <-> ee
  \path (ee) edge[bend left=10] node [above] {\^{R3}} (pm);
  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);

  %ga->pm
  \path (ga) edge[bend left=10] node [right] {{Qb2} Qc2} (pm);
  \path (ga) edge[bend left=80] node [above] {\^{R2}} (pm);
  \path (ga) edge[bend left=52] node [above] {\^{R7}} (pm);
  \path (ga) edge[bend left] node [above] {\^{R8}} (pm);
  \end{tikzpicture}
  \caption{found-in-nature VTS}
  \label{fig:mukund-vts}
\end{figure}

In figure~\ref{fig:mukund-vts}

The figure~\ref{fig:mukund} represent mammalian SNARE map created by studying the references []. In this diagram the gray circles represent compartments, the identities of compartments are
written within: ER=endoplasmic reticulum, ERGIC=ER-Golgi intermediate compartment,
RE=recycling endosome, EE=early endosome, LE=late endosome, LYS=lysosome, PM=plasma
membrane. Thin black arrows represent vesicle edges.
% and hollow arrows represent maturation edges. 
The set of SNAREs contained in these edges are written alongside each edge. Actual names
of these SNAREs are mentioned in the key alongside. The red labels represent the paths taken by
SNARES of the complex Stx-4-SNAP23-VAMP7. Here, the cycles for two SNARE molecules,
VAMP7 and SNAP23 are complete. The green labels represent the paths taken by SNAREs of the
complex Stx13-SNAP25-VAMP2. Here the cycle for VAMP2 is complete.The blue labels represent
the paths taken by SNARES of the complex Stx5-Gs28-Bet1/GS15-Ykt6. Here, cycles for none of
the SNAREs are complete.

>>>>

@@

  % \path (ic) edge node [below] {\^{Qc6}} (ga);
  % \path (er) edge[bend right=20] node [right] {\^{Qc6}} (ic);

  % %er <> ga
  % \path (er) edge[bend right=20] node [left] {\^{Qc6}} (ga);
  % \path (er) edge[bend left=20] node [left] {R6} (ga);
  % \path (ga) edge[bend right=40] node [left] {\^{Qc1}} (er);

  % %ga <-> ee
  % \path (ga) edge[bend left=25] node [above] {Qb2 Qc2} (ee);
  % \path (ga) edge[bend left=10] node [above] {Qbc2/3} (ee);
  % \path (ee) edge[bend left=0] node [below] {Qb2/3,Qa2,R2,\^{R4},Qc2/3} (ga);

  % %le <-> pm
  % \path (le) edge[bend right=10] node [above] {Qb7 Qc7} (pm);
  % %ee -> le
  % \path (ee) edge[bend right] node [below,rotate=70] {\^{R8},Qa7,Qbc7,R7} (le);

  % %pm <-> ee
  % \path (ee) edge[bend left=10] node [above] {\^{R3}} (pm);
  % \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);

  % %ga->pm
  % \path (ga) edge[bend left=10] node [right] {{Qb2} Qc2} (pm);
  % \path (ga) edge[bend left=80] node [above] {\^{R2}} (pm);
  % \path (ga) edge[bend left=52] node [above] {\^{R7}} (pm);
  % \path (ga) edge[bend left] node [above] {\^{R8}} (pm);
  \end{tikzpicture}
  \caption{found-in-nature VTS}
  \label{fig:mukund-vts}
\end{figure}

### 2018-05-04 papers/synth/related.tex
my fusion added

In recent years, there has been a wide range of methods
developed for the similar synthesis problems~\cite{sktech,ceSynth,exampleSynth}.

>>>>

In recent years, there has been a wide range of methods
developed for the similar synthesis problems~\cite{sktech,cegis,exampleSynth}.
%
They range from filling gaps an implementation of C programs from the
pool of template predicates to learn learn an a program from example
runs of the program.
%
In the course of developing such methods,
the background technology, i.e. solving of quantified
constraints,~\cite{depQBF,Z3quantifier,markusRabeSolver} has been evolving rapidly.
